Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-17 paper/paperv3.qmd
Fixing an error in the mapping for h4 sensitivity tests

  # H4
molt_data <- sealdat %>% 
  filter(year >= 2011, 
         moltdur >= 7, 
         age <= 20) %>% 
  mutate(BA = firstobsbreeddoy, 
         BD = firstobsbreeddoy + breeddur, 
         MA = lastobsmoltdoy - moltdur, 
         MD = lastobsmoltdoy) %>% 
  drop_na(age, BA, BD, MA, MD) %>% 
  transmute(animalID, 
            year_fct, 
            age10 = (age - age_senesce) / 10, 
            age_cat = factor(age >= age_senesce, 
                          labels = c("Young", "Old")),
            moltdur, 
            breeddur) %>% 
  pivot_longer(moltdur:breeddur, 
               names_to = "phase", 
               values_to = "dur_days") %>% 
  filter(phase == "moltdur")

molt_mod <- glmer(dur_days ~ age10 : age_cat + (1 | year_fct) + (1 | animalID), 
        molt_data, 
        family = Gamma(link = "log"))

breed_data <- sealdat %>% 
  filter(year >= 2011, 
         moltdur >= 7, 
         age <= 20) %>% 
  mutate(BA = firstobsbreeddoy, 
         BD = firstobsbreeddoy + breeddur, 
         MA = lastobsmoltdoy - moltdur, 
         MD = lastobsmoltdoy) %>% 
  drop_na(age, BA, BD, MA, MD) %>% 
  transmute(animalID, 
            year_fct, 
            age10 = (age - age_senesce) / 10, 
            age_cat = factor(age >= age_senesce, 
                          labels = c("Young", "Old")),
            moltdur, 
            breeddur) %>% 
  pivot_longer(moltdur:breeddur, 
               names_to = "phase", 
               values_to = "dur_days") %>% 
  filter(phase == "breeddur")

breed_mod <- glmer(dur_days ~ age10 : age_cat + (1 | year_fct) + (1 | animalID), 
        data = breed_data, 
        family = Gamma(link = "log"), 
        control = glmerControl(optimizer = "bobyqa")
)

@@

# Fit models with cut-off at ages 8-13
cutoff <- 6:14
mod_sens <- map(cutoff, fit_models)

>>>>

  # H4
  pheno_data <- sealdat %>% 
    filter(year >= 2011, 
           moltdur >= 7, 
           age <= 20) %>% 
    mutate(BA = firstobsbreeddoy, 
           BD = firstobsbreeddoy + breeddur, 
           MA = lastobsmoltdoy - moltdur, 
           MD = lastobsmoltdoy) %>% 
    drop_na(age, BA, BD, MA, MD) %>% 
    select(animalID,
           age10,
           age_cat,
           year_fct,
           moltdur, 
           breeddur) %>% 
    pivot_longer(moltdur:breeddur, 
                 names_to = "phase", 
                 values_to = "dur_days")

  molt_mod <- glmer(dur_days ~ age10 : age_cat + (1 | year_fct) + (1 | animalID), 
                    filter(pheno_data, phase == "moltdur"), 
                    family = Gamma(link = "log"))

  breed_mod <- glmer(dur_days ~ age10 : age_cat + (1 | year_fct) + (1 | animalID), 
                     filter(pheno_data, phase == "breeddur"), 
                     family = Gamma(link = "log"), 
                     control = glmerControl(optimizer = "bobyqa"))

@@

# Fit models with cut-off at ages 6-14
cutoff <- 6:14
mod_sens <- map(cutoff, fit_models)
